\subsection{Purpose}
The purpose of the DD is to provide a strategic guide to develop the project in the correct way, avoiding the errors and the waste of time that could be generated without studing the problem and the possible solutions. 
The document will be given to the development team.

\subsubsection{Scope}
The web platform will provide a system that manage the reports of the parking violations and elaborates the data to retrieve information about streets and cars:
\begin{itemize}
	\item
	Report violation
	\item 
	Report validation
	\item
	Update statistics
	\item
	Manage streets data
	\item
	Different usage between end user and authority
\end{itemize}
\subsection{Definitions, Acronyms, Abbreviations}
\subsubsection{Definitions}
\begin{itemize}
	\item 
	End-user: The end-user is the common user of the application, that takes pictures of violations and send it with all the report data to the system.
	\item 
	Authority: Authorities are public entities, e.g. municipality, they use SafeStreets in order to see statistics, consult possible interventions and get information about traffic violations.
	
	
	Furthermore they can retrieve data in order to generate traffic tickets with their own systems.
	\item 
	Web Server: A Web server uses HTTP (Hypertext Transfer Protocol) to provide the files that compose the Web pages to users. The requests are forwarded by their clients HTTP.
	 
	Dedicated computers and appliances may be referred to as Web servers as well.
	\item 
	Application Server: An application server is a type of server designed to install, operate and host applications and associated services for end users, IT services and organizations.
\end{itemize}
\subsubsection{Acronyms}
\begin{itemize}
	\item
	API: Application Programming Interface
	\item
	DD: Design Document
	\item
	JDBC: Java DataBase Connectivity
	\item
	RASD: Requirements Analysis and Specifications Document
	\item
	UX: User Experience
	\item
	ANPR: Automatic number-plate recognition
	\item
	CUU: Code Unique Unitary
	\item 
	JSON: JavaScript Object Notation
	\item
	REST: Representational State Transfer
	\item 
	RDBMS: Relational DataBase Management System
\end{itemize}

